---
title:  "Code Chalange Tenchi Security"
author:   "João L M Resende"
date:   "30 january 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(knitr)

```

# Report for Abin 
This is a report to show about cyber breach information. 
```{r load data, include=FALSE}
sample_breaches <- read.csv("sample_breaches.csv")
```

## Summary of the Data

```{r sample_breaches, echo=FALSE}
summary(sample_breaches)
```

  This data shows that the mean value of each breach is **\$`r format(mean(sample_breaches$total_amount), scientific = FALSE, big.mark = ",")` **. Te minimum value of the breach is **\$`r format(min(sample_breaches$total_amount), scientific = FALSE, big.mark = ",")` **, and he maximum value is **\$`r format(max(sample_breaches$total_amount), scientific = FALSE, big.mark = ",")` **
  
The 5 sectors which more occurrence of breach of information are shown in the table below:

```{r, echo=FALSE}

freq_sector <- sample_breaches %>% 
  group_by(sector) %>% 
  count(sort = TRUE, name = "Occurrence")

kable(head(freq_sector,5), caption = "Ocurrence per secto")

```

As we can see, the **`r head(freq_sector$sector,1)`** is the leader of breach of information, with **`r head(freq_sector$Occurrence,1)`** occurrence.  Now, in the plot below we can see the division between external and internal causes.  

```{r, include=FALS}

sample_breaches <- sample_breaches %>% 
  mutate(causes_int_ext = str_extract(cause, "[^ -]*"))#creation of column to divide causes in externals and internals

sample_breaches %>% 
  group_by(causes_int_ext) %>% 
  count(sort = TRUE, name = "Occurrence") %>% 
  ggplot(aes(causes_int_ext, Occurrence, fill = causes_int_ext))+
  geom_col()

```


You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
